KidsAIR: Main analysis initial steps

### 2020-09-28 main_analysis_initial.Rmd
main analysis updates

---
title: "KidsAIR: Main analysis initial steps"
author: "Ethan Walker"
date: "Started 23 Sept 2020, Updated 23 Sept 2020"
output: pdf_document
header-includes:
    - \usepackage[labelformat=empty]{caption}
---

@@

lrti_final_data <- read_rds(paste0(file_path, "Output/lrti_final_data.rds")) %>% 
  group_by(area, home_winter_id, child_id_num) %>% 
  mutate(lrti_events = n(),
         person_time_no_lrti_total = as.numeric(person_time_no_lrti_total),
         lrti_incidence = lrti_events/person_time_no_lrti_total*7,
         lrti_incidence = if_else(is.na(lrti_incidence), 0, lrti_incidence))
```

```{r}
# Merge dataset with blinded treatments and final LRTI data, select analysis variables
analysis_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>% 
  right_join(lrti_final_data, by = c("area", "child_id_num", "home_winter_id")) %>% 
  distinct(area, child_id_num, home_winter_id, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, )

```

>>>>

---
title: "KidsAIR: Main analysis initial steps"
author: "Ethan Walker"
date: "Started 23 Sept 2020, Updated 28 Sept 2020"
output: pdf_document
header-includes:
    - \usepackage[labelformat=empty]{caption}
---

@@

lrti_final_data <- read_rds(paste0(file_path, "Output/lrti_final_data.rds")) %>% 
  arrange(area, home, child_id_num, winter_id) %>% 
  mutate(cohort = round_date(csq_date, unit = "year")) %>% 
  separate(cohort, c("cohort", "trash"), sep = "-") %>% 
  group_by(area, child_id_num, home_winter_id) %>% 
  mutate(lrti_events = n()) %>% 
  group_by(area, child_id_num) %>% 
  distinct(area, child_id_num, home_winter_id, .keep_all = TRUE) %>% 
  mutate(lrti_events = as.numeric(lrti_events),
         lrti_events = if_else(is.na(person_time_no_lrti_total), 0, lrti_events),
         lrti_events_total = sum(lrti_events, na.rm = TRUE),
         person_time_no_lrti_total = as.numeric(person_time_no_lrti_total),
         time_at_risk_total = sum(person_time_no_lrti_total, na.rm = TRUE),
         lrti_incidence = lrti_events_total/sum(time_at_risk_total)*7,
         lrti_incidence = if_else(is.na(lrti_incidence), 0, lrti_incidence)) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  select(area, home, cohort, child_id_num, lrti_events_total, time_at_risk_total, lrti_incidence)
```

```{r}
# Merge dataset with blinded treatments and final LRTI data, select analysis variables
analysis_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>% 
  right_join(lrti_final_data, by = c("area", "home", "child_id_num")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  select(area, home, cohort, child_id_num, lrti_events_total, time_at_risk_total, lrti_incidence, newtx) %>% 
  rename(treatment = newtx)
```

```{r}
# Initial summary data for LRTI
incidence_summary <- analysis_data %>% 
  group_by(treatment) %>% 
  summarize(mean_inc = mean(lrti_incidence, na.rm = TRUE),
            sd_inc = sd(lrti_incidence, na.rm = TRUE),
            min_inc = min(lrti_incidence, na.rm = TRUE),
            median_inc = median(lrti_incidence, na.rm = TRUE),
            max_inc = max(lrti_incidence, na.rm = TRUE))
incidence_summary
```

```{r}
model_results <- glmer(lrti_incidence ~ treatment + (1 | home:cohort:area), data = analysis_data, family = poisson(link = "log"))

summary(model_results)
```
